---
title: "lab4_code_along_part1"
author: "Danielle Sclafani"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Confidence Interval in a sample

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```

the default setting of the above, gives you the pvalue when Hnull = 0 (probability of getting a sample with otter length of 0 inches, doesnt really make sense becuase you would never have an otter with a length of 0 but that is just the default of the above formula )

if you type in consol ?t.test and hit enter, it will bring up a description of the function and its default


## T-Test (1-sample t-test)

we can specify the mean we want to test - need to change the mu=
See a claim that the mean otter length is 50 inches. We want to test that

```{r}
otter_test <- t.test(x=otter_length, # x is the sample, so x=sample, sample in this case is otter_length #using the storing operator <-, the data is being stored in the environment
                     mu=50) # the mean you are testing

t.test(x=otter_length, # do it without the storage operator for the data to come up below
                     mu=50)
```

If pop mean really is 50 inches, then there is a 4.4% probability, that we could have taken a sample with a mean this far away in either direction (~8 inches away, because out sample mean is 42.2)


##. Two sample t-test

two herds of big horn sheep

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x=desert_bighorns, y=sierra_bighorns) #first sample is x, second sample is y

```

confidence internal can be negative, because this is the confidence interval of the difference of the means of the two bighorns

this test was testing that the difference in means was equal to 0. 
p-value =0.88 - this means that there is an 88% probability we could get means that are at least this different if they were drawn from populations with the same mean. --> this means there is a good chance that the two populations have the same mean - not enough evidence to reject null hypothesis

END PART 1

## Part 2. Two sample t-test

create a subset of data for the two classes of cars we are interested in (SUV and compacts)

```{r}
suv_compact <- mpg %>% 
  filter(class %in% c("suv", "compact")) # %in% means match anything in
```


## Exploratory Data visualization using ggplot

exploratory histograms --> because important to have a visualization of the distribution of our data

```{r}
ggplot(data= suv_compact, aes(x= cty)) +
  geom_histogram(bins = 15) +
  facet_wrap(~class) #facet wrap by group, this gives you two histograms for each car class, first step at looking at distributions of samples
```

Using a quantile-quantile plot (QQplot) -->  graphs your sample against a perfectly normal distribution- see how linear this relationship is


```{r}
ggplot(data=suv_compact, aes(sample= cty)) +
  geom_qq() +
  facet_wrap(~class) 
# suv looks pretty linear, compact is a little curved pretty much linear except for a few at the top that have better gas mileage- slight positive skew
```

## Descriptive statistics

```{r}
car_stats <- suv_compact %>% 
  group_by(class) %>%  
  summarize(mean_city = mean(cty), #give me a summary stat of the mean_city gas mileage, using =mean(cty) tells R to calculate the mean and name it mean_city
           sd_city =sd(cty), # standard deviation of city gas mileage
           n = n()) #calculates number of observations in each group 

car_stats
```

care about sample size, the larger the sample size gets the closer our sample distribution will be to normal. Even if our graphic visual distributions do not look normal, if n is greater than 30, because of the central limit theorem, we can still use a t-test to compare the means

## 2-sample t-test

create my vectors containing observations for each sample (City gas mileage)
```{r}
compact_sample <- suv_compact %>% 
  filter(class == "compact") %>% #filtering to compact 
  pull(cty) #takes a single column and makes a vector, if you use select it will keep it stored as a data frame. t test needs a vector not a data frame

suv_sample <- suv_compact %>% 
  filter(class == "suv") %>% 
  pull(cty)
  
t.test(x=compact_sample, y=suv_sample)

```









