---
title: "lab4_code_along_part1"
author: "Danielle Sclafani"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Confidence Interval in a sample

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)
```

the default setting of the above, gives you the pvalue when Hnull = 0 (probability of getting a sample with otter length of 0 inches, doesnt really make sense becuase you would never have an otter with a length of 0 but that is just the default of the above formula )

if you type in consol ?t.test and hit enter, it will bring up a description of the function and its default


## T-Test (1-sample t-test)

we can specify the mean we want to test - need to change the mu=
See a claim that the mean otter length is 50 inches. We want to test that

```{r}
otter_test <- t.test(x=otter_length, # x is the sample, so x=sample, sample in this case is otter_length #using the storing operator <-, the data is being stored in the environment
                     mu=50) # the mean you are testing

t.test(x=otter_length, # do it without the storage operator for the data to come up below
                     mu=50)
```

If pop mean really is 50 inches, then there is a 4.4% probability, that we could have taken a sample with a mean this far away in either direction (~8 inches away, because out sample mean is 42.2)


##. Two sample t-test

two herds of big horn sheep

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x=desert_bighorns, y=sierra_bighorns) #first sample is x, second sample is y

```

confidence internal can be negative, because this is the confidence interval of the difference of the means of the two bighorns

this test was testing that the difference in means was equal to 0. 
p-value =0.88 - this means that there is an 88% probability we could get means that are at least this different if they were drawn from populations with the same mean. --> this means there is a good chance that the two populations have the same mean - not enough evidence to reject null hypothesis
